Estimating Neighborhood Rents with Scraped Data

### 2018-08-01 manuscript/index.Rmd
updating analysis to drop rent field from unique listing definition

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  theme(legend.key.width = unit(.1, "inch")) +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 3, dpi =300)
```

@@

```{r avp_map_series, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
obs_map_series <- ggplot(sea_f, aes(x = long, y = lat, group = group, fill = actualRent)) +
  facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(labels = scales::dollar, na.value = "grey80",
                       limits = c(800, 2800), option = "A") +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank(),
        legend.position = "top") +
  guides(fill = "none") +
  labs(subtitle = "Observed", fill = "1B Rent")

bym_map_series <- ggplot(sea_f, aes(x = long, y = lat, group = group, fill = bym_Med)) +
  facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(labels = scales::dollar, na.value = "grey80",
                       limits = c(800, 2800), option = "A") +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank(),
        legend.position = "bottom",
        legend.key.height = unit(.1, "inch")) +
  guides(fill = guide_colourbar(barwidth = 15,
       label.position = "bottom")) +
  labs(subtitle = "Spatial AR(1) Prediction", fill = "1B Rent")

>>>>

ggplot(bym_df %>% filter(model == "E. Spatial AR(1)"), 
         aes(x = listingQtr, y = value, group = GISJOIN, color = qtrDev, label = GISJOIN)) +
  geom_line(lwd = .25, color = "black", alpha = .5) +
  geom_point() +
  scale_y_continuous(labels = scales::dollar) +
  scale_color_viridis_c(option = "A", labels = scales::dollar, direction = -1) +
  xlab("") +
  ylab("Median 1B Rent\n") +
  labs(color="Quarterly\nDeviation") +
  theme_minimal() +
  theme(legend.key.width = unit(.1, "inch")) +
  ggsave(filename = "../output/bym_lineplot.png",
         width = 6, height = 3, dpi =300)
```

@@

```{r avp_map_series, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
obs_map_series <- ggplot(sea_f, aes(x = long, y = lat, group = group, fill = actualRent)) +
  facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(labels = scales::dollar, na.value = "grey80",
                       limits = c(800, 2800), option = "A", direction = -1) +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank(),
        legend.position = "top") +
  guides(fill = "none") +
  labs(subtitle = "Observed", fill = "1B Rent")

bym_map_series <- ggplot(sea_f, aes(x = long, y = lat, group = group, fill = bym_Med)) +
  facet_grid(~ listingQtr) +
  geom_polygon(color = "grey85", lwd = .05) +
  scale_fill_viridis_c(labels = scales::dollar, na.value = "grey80",
                       limits = c(800, 2800), option = "A", direction = -1) +
  coord_quickmap() +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank(),
        legend.position = "bottom",
        legend.key.height = unit(.1, "inch")) +
  guides(fill = guide_colourbar(barwidth = 15,
       label.position = "bottom")) +
  labs(subtitle = "Spatial AR(1) Prediction", fill = "1B Rent")

### 2018-08-01 manuscript/manuscript.Rmd
updating analysis to drop rent field from unique listing definition

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess and Sarah Chasins"
output:
  html_document:
    df_print: paged
abstract: Online classified ads are a key source of information about local rental
  housing markets. This research first assesses the agreement of census tract rent
  estimates based on scraped rental advertisements with existing data sources. The
  second component of the paper investigates temporal and spatial dynamics in one-bedroom
  rents among Seattle neighborhoods using spatial models. Posterior distributions
  of all model hyperparameters and parameters are estimated with integrated nested
  Laplace approximations (INLA). Training data for models cover quarterly tract estimates
  for Q2 2017 through Q1 2018, while the test data are Q2 2018 median values as observed.
  The top model assumes that spatial and temporal dynamics are separable, i.e. independent
  of each other, and non-interactive. This spatial random-effects model with AR(1)
  temporal structure achieves a mean absolute error (MAE) of about $100 for the training
  data and $140 for the test data.
---

>>>>

---
title: "Estimating Neighborhood Rents with Scraped Data"
author: "Chris Hess and Sarah Chasins"
output:
  pdf_document:
    df_print: paged
abstract: Online classified ads are a key source of information about local rental
  housing markets. This research first assesses the agreement of census tract rent
  estimates based on scraped rental advertisements with existing data sources. The
  second component of the paper investigates temporal and spatial dynamics in one-bedroom
  rents among Seattle neighborhoods using spatial models. Posterior distributions
  of all model hyperparameters and parameters are estimated with integrated nested
  Laplace approximations (INLA). Training data for models cover quarterly tract estimates
  for Q2 2017 through Q1 2018, while the test data are Q2 2018 median values as observed.
  The top model assumes that spatial and temporal dynamics are separable, i.e. independent
  of each other, and non-interactive. This spatial random-effects model with AR(1)
  temporal structure achieves a mean absolute error (MAE) of about $100 for the training
  data and $140 for the test data.
---
